---
title: "Primary_outcomes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Primary_outcomes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figs/",
  fig.height = 6,
  fig.width = 8,
  fig.align = "center",
  warning=FALSE
)
```

## Load data

```{r load}
#library(librarian)
#librarian::shelf(here, readxl, metafor, quiet = TRUE)

dat <- readxl::read_excel(here::here("data", "Dex_metan.xlsx"),
                  range = "B3:T11",
                  col_names=c("study", "n1i", "n2i",
                              "ai_atel", "bi_atel", "ci_atel", "di_atel",
                              "ai_pneu", "bi_pneu", "ci_pneu", "di_pneu",
                              "ai_hypo", "bi_hypo", "ci_hypo", "di_hypo",
                              "ai_ards", "bi_ards", "ci_ards", "di_ards")
                  )
print(dat, width=Inf)
```
Removed final row, containing no data (for Lee et al.)

## Main Analysis
### Atelectasis

```{r atelectasis}
dat.atelectasis <- metafor::escalc(measure="OR",
                          ai=ai_atel,
                          bi=bi_atel,
                          ci=ci_atel,
                          di=di_atel,
                          data=dat,
                          slab = study)
pm.atelectasis <- metafor::rma(yi, vi, data=dat.atelectasis, method="PM")
metafor::forest(pm.atelectasis,
       atransf=exp,
       at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 2, 5, 10)))
```

### Pneumonia
```{r pneumonia}
dat.pneumonia <- metafor::escalc(measure="OR",
                          ai=ai_pneu,
                          bi=bi_pneu,
                          ci=ci_pneu,
                          di=di_pneu,
                          data=dat,
                          slab = study)

pm.pneumonia <- metafor::rma(yi, vi, data=dat.pneumonia, method="PM")
metafor::forest(pm.pneumonia,
       atransf=exp,
       at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 2, 5, 10)))
```

### Hypoxemia
```{r hypoxemia}
dat.hypoxemia <- metafor::escalc(measure="OR",
                        ai=ai_hypo,
                        bi=bi_hypo,
                        ci=ci_hypo,
                        di=di_hypo,
                        data=dat,
                        slab = study)

pm.hypoxemia <- metafor::rma(yi, vi, data=dat.hypoxemia, method="PM")
metafor::forest(pm.hypoxemia,
       atransf=exp,
       at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 2, 5, 10)))
```

### ARDS
```{r ARDS}
dat.ards <- metafor::escalc(measure="OR",
                        ai=ai_ards,
                        bi=bi_ards,
                        ci=ci_ards,
                        di=di_ards,
                        data=dat,
                        slab = study)

pm.ards <- metafor::rma(yi, vi, data=dat.ards, method="PM")
metafor::forest(pm.ards,
       atransf=exp,
       at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 2, 5, 10)))
```
Note: n=3 here, but n=2 in metafor::forest plot in PDF. Which is correct?


## Sensitivity Analysis
HKSJ correction results in narrower CIs:
```{r hksj atel}
pmhk.atelectasis <- metafor::rma(yi, vi, data=dat.atelectasis, method="PM", test="knha")
metafor::forest(pmhk.atelectasis,
                atransf=exp,
                at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 1, 2, 5, 10)),
                ilab = cbind(ai_atel, n1i, bi_atel, n2i),
                ilab.xpos = c(-9.5,-8.5,-7.5,-6.5),
                cex=.75, header=c("Author(s) and Year"),
                xlab=""
)
text(c(-9.5,-8.5,-7.5,-6.5), pmhk.atelectasis$k+1.5, c("E", "T", "E", "T"), cex=0.75)
text(c(-9,-7),     pmhk.atelectasis$k+2, c("Dexmed.", "Placebo"), cex=0.75)
par(xpd=NA)
text(log(c(0.001, 45)), -4, c("Favours Dexmedetomidine","Favours Placebo"), pos=c(4,2), offset=-0.5, cex=0.75)
```

```{r hksj pneu}
pmhk.pneumonia <- metafor::rma(yi, vi, data=dat.pneumonia, method="PM", test="knha")
metafor::forest(pmhk.pneumonia,
                atransf=exp,
                at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 1, 2, 5, 10)),
                ilab = cbind(ai_pneu, n1i, bi_pneu, n2i),
                ilab.xpos = c(-9.5,-8.5,-7.5,-6.5)+1.75,
                cex=.75, header=c("Author(s) and Year"),
                xlab=""
)
text(c(-9.5,-8.5,-7.5,-6.5)+1.75, pmhk.pneumonia$k+1.5, c("E", "T", "E", "T"), cex=0.75)
text(c(-9,-7)+1.75,     pmhk.pneumonia$k+2, c("Dexmed.", "Placebo"), cex=0.75)
par(xpd=NA)
text(log(c(0.005, 45)), -4, c("Favours Dexmedetomidine","Favours Placebo"), pos=c(4,2), offset=-0.5, cex=0.75)
```

```{r hksj hypox}
pmhk.hypoxemia <- metafor::rma(yi, vi, data=dat.hypoxemia, method="PM", test="knha")
# metafor::forest(pmhk.hypoxemia,
#        atransf=exp,
#        at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 2, 5, 10)))
metafor::forest(pmhk.hypoxemia,
                atransf=exp,
                at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 1, 2, 5, 10)),
                ilab = cbind(ai_hypo, n1i, bi_hypo, n2i),
                ilab.xpos = c(-7.5,-7,-6.5,-6)+1.75,
                cex=.75, header=c("Author(s) and Year"),
                xlab=""
)
text(c(-7.5,-7,-6.5,-6)+1.75, pmhk.hypoxemia$k+1.5, c("E", "T", "E", "T"), cex=0.75)
text(c(-7.25,-6)+1.75,     pmhk.hypoxemia$k+2, c("Dexmed.", "Placebo"), cex=0.75)
par(xpd=NA)
text(log(c(0.005, 40)), -3, c("Favours Dexmedetomidine","Favours Placebo"), pos=c(4,2), offset=-0.5, cex=0.75)
```

```{r hksj ARDS}
pmhk.ards <- metafor::rma(yi, vi, data=dat.ards, method="PM", test="knha")
# metafor::forest(pmhk.ards,
#        atransf=exp,
#        at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 2, 5, 10)))
metafor::forest(pmhk.ards,
                atransf=exp,
                at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 1, 2, 5, 10)),
                ilab = cbind(ai_ards, n1i, bi_ards, n2i),
                ilab.xpos = c(-9.5,-8.5,-7.5,-6.5)+1.75,
                cex=.75, header=c("Author(s) and Year"),
                xlab=""
)
text(c(-9.5,-8.5,-7.5,-6.5)+1.75, pmhk.ards$k+1.5, c("E", "T", "E", "T"), cex=0.75)
text(c(-9,-7)+1.75,     pmhk.ards$k+2, c("Dexmed.", "Placebo"), cex=0.75)
par(xpd=NA)
text(log(c(0.005, 45)), -3.5, c("Favours Dexmedetomidine","Favours Placebo"), pos=c(4,2), offset=-0.5, cex=0.75)
```


## Funnel plots
```{r funnels}
# Atelectasis:
### carry out trim-and-fill analysis
taf.atelectasis <- metafor::trimfill(pm.atelectasis)
### draw funnel plot with missing studies filled in
metafor::funnel(taf.atelectasis, legend=TRUE)
# OR and CI:
exp(taf.atelectasis$beta)
c(exp(taf.atelectasis$beta-taf.atelectasis$se), exp(taf.atelectasis$beta+taf.atelectasis$se))

# Pneumonia
taf.pneumonia <- metafor::trimfill(pm.pneumonia)
metafor::funnel(taf.pneumonia, legend=TRUE)
# OR and CI:
exp(taf.pneumonia$beta)
c(exp(taf.pneumonia$beta-taf.pneumonia$se), exp(taf.pneumonia$beta+taf.pneumonia$se))
```

Trim-and-fill analysis on the atelectasis meta-analysis data estimates that there 
are three studies missing. Removing the most extreme studies until there is no 
asymmetry results in a summary estimate of 0.60 (95% CI (0.41, 0.88)), which is
smaller but still statistically significant. However, we acknowledge that this 
procedure 
the total number of studies is small, 
