---
title: "Primary_outcomes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Primary_outcomes}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figs/",
  fig.height = 6,
  fig.width = 8,
  fig.align = "center",
  warning=FALSE
)
```

## Load data

```{r load}
#library(librarian)
#librarian::shelf(here, readxl, metafor, quiet = TRUE)

dat <- readxl::read_excel(here::here("data", "Dex_metan.xlsx"),
                  range = "B3:AB11",
                  col_names=c("study", "n1i", "n2i",
                              "ai_atel", "bi_atel", "ci_atel", "di_atel", "per_dex_atel", "per_con_atel", 
                              "ai_pneu", "bi_pneu", "ci_pneu", "di_pneu", "per_dex_pneu", "per_con_pneu", 
                              "ai_hypo", "bi_hypo", "ci_hypo", "di_hypo", "per_dex_hypo", "per_con_hypo", 
                              "ai_ards", "bi_ards", "ci_ards", "di_ards", "per_dex_ards", "per_con_ards")
                  )
print(dat, width=Inf)
```
Did not include final two rows containing Quingming et al., as these are not included in the meta-analysis paper.

Wu et al. is missing sample size data. The sample size is 30 on each arm, and can be inferred by the pneumonia data. Add this:

```{r correct dat}
wu.row <- which(dat$study=="Wu et al")
dat[wu.row, "n1i"] <- 30
dat[wu.row, "n2i"] <- 30
```


## Descriptive statistics
### Atelectasis
```{r descriptive atel, echo=FALSE}
study.index.atel <- which(!is.na(dat$ai_atel))
dat.atel <- dat[study.index.atel, c("n1i", "n2i",
                        "ai_atel", "bi_atel", "ci_atel", "di_atel")]
sums.atel <- colSums(dat.atel)

risk.atel.dex <- sums.atel["ai_atel"]/sums.atel["n1i"]
risk.atel.con <- sums.atel["bi_atel"]/sums.atel["n2i"]
risk.diff.atel <- risk.atel.con - risk.atel.dex
risk.ratio.atel <- risk.atel.dex/risk.atel.con
```
For Atelectasis: risk on dex is `r round(100*risk.atel.dex, 1)`%, risk on control is  `r round(100*risk.atel.con, 1)`%. Risk difference is  `r round(100*risk.diff.atel, 1)`%, risk ratio is `r round(risk.ratio.atel, 2)`.

### Pneumonia
```{r descriptive pneu, echo=FALSE}
study.index.pneu <- which(!is.na(dat$ai_pneu))
dat.pneu <- dat[study.index.pneu, c("n1i", "n2i",
                        "ai_pneu", "bi_pneu", "ci_pneu", "di_pneu")]
sums.pneu <- colSums(dat.pneu)

risk.pneu.dex <- sums.pneu["ai_pneu"]/sums.pneu["n1i"]
risk.pneu.con <- sums.pneu["bi_pneu"]/sums.pneu["n2i"]
risk.diff.pneu <- risk.pneu.con - risk.pneu.dex
risk.ratio.pneu <- risk.pneu.dex/risk.pneu.con
```
For pneumonia: risk on dex is `r round(100*risk.pneu.dex, 1)`%, risk on control is  `r round(100*risk.pneu.con, 1)`%. Risk difference is  `r round(100*risk.diff.pneu, 1)`%, risk ratio is `r round(risk.ratio.pneu, 2)`.

### Hypoxemia
```{r descriptive hypo, echo=FALSE}
study.index.hypo <- which(!is.na(dat$ai_hypo))
dat.hypo <- dat[study.index.hypo, c("n1i", "n2i",
                        "ai_hypo", "bi_hypo", "ci_hypo", "di_hypo")]
sums.hypo <- colSums(dat.hypo)

risk.hypo.dex <- sums.hypo["ai_hypo"]/sums.hypo["n1i"]
risk.hypo.con <- sums.hypo["bi_hypo"]/sums.hypo["n2i"]
risk.diff.hypo <- risk.hypo.con - risk.hypo.dex
risk.ratio.hypo <- risk.hypo.dex/risk.hypo.con
```
For hypomonia: risk on dex is `r round(100*risk.hypo.dex, 1)`%, risk on control is  `r round(100*risk.hypo.con, 1)`%. Risk difference is  `r round(100*risk.diff.hypo, 1)`%, risk ratio is `r round(risk.ratio.hypo, 2)`.



### ARDS
```{r descriptive ards, echo=FALSE}
study.index.ards <- which(!is.na(dat$ai_ards))
dat.ards <- dat[study.index.ards, c("n1i", "n2i",
                        "ai_ards", "bi_ards", "ci_ards", "di_ards")]
sums.ards <- colSums(dat.ards)

risk.ards.dex <- sums.ards["ai_ards"]/sums.ards["n1i"]
risk.ards.con <- sums.ards["bi_ards"]/sums.ards["n2i"]
risk.diff.ards <- risk.ards.con - risk.ards.dex
risk.ratio.ards <- risk.ards.dex/risk.ards.con
```
For ardsmonia: risk on dex is `r round(100*risk.ards.dex, 1)`%, risk on control is  `r round(100*risk.ards.con, 1)`%. Risk difference is  `r round(100*risk.diff.ards, 1)`%, risk ratio is `r round(risk.ratio.ards, 2)`.


## Main Analysis
### Atelectasis

```{r atelectasis}
class(dat$ai_atel)
class(dat$ai_pneu)
class(dat$ai_hypo)
class(dat$ai_ards)

test.dat <- dat[study.index.atel, c("study", "n1i", "n2i",
                        "ai_atel", "bi_atel", "ci_atel", "di_atel")]
dat.atelectasis <- metafor::escalc(measure="OR",
                          ai=ai_atel,
                          bi=bi_atel,
                          ci=ci_atel,
                          di=di_atel,
                          data=test.dat, # XXXXX
                          slab = study)
pm.atelectasis <- metafor::rma(yi, vi, data=dat.atelectasis, method="PM")
# metafor::regtest(pm.atelectasis)
# metafor::regtest(pm.atelectasis, model="lm")
metafor::forest(pm.atelectasis,
       atransf=exp,
       at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 2, 5, 10)))
```

### Pneumonia
```{r pneumonia}
dat.pneumonia <- metafor::escalc(measure="OR",
                          ai=ai_pneu,
                          bi=bi_pneu,
                          ci=ci_pneu,
                          di=di_pneu,
                          data=dat,
                          slab = study)

pm.pneumonia <- metafor::rma(yi, vi, data=dat.pneumonia, method="PM")
# metafor::regtest(pm.pneumonia)
# metafor::regtest(pm.pneumonia, model="lm")
metafor::forest(pm.pneumonia,
       atransf=exp,
       at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 2, 5, 10)))
```

### Hypoxemia
```{r hypoxemia}
dat.hypoxemia <- metafor::escalc(measure="OR",
                        ai=ai_hypo,
                        bi=bi_hypo,
                        ci=ci_hypo,
                        di=di_hypo,
                        data=dat,
                        slab = study)

pm.hypoxemia <- metafor::rma(yi, vi, data=dat.hypoxemia, method="PM")
# metafor::regtest(pm.hypoxemia)
# metafor::regtest(pm.hypoxemia, model="lm")
metafor::forest(pm.hypoxemia,
       atransf=exp,
       at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 2, 5, 10)))
```

### ARDS
```{r ARDS}
dat.ards <- metafor::escalc(measure="OR",
                        ai=ai_ards,
                        bi=bi_ards,
                        ci=ci_ards,
                        di=di_ards,
                        data=dat,
                        slab = study)

pm.ards <- metafor::rma(yi, vi, data=dat.ards, method="PM")
# metafor::regtest(pm.ards)
# metafor::regtest(pm.ards, model="lm")
metafor::forest(pm.ards,
       atransf=exp,
       at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 2, 5, 10)))
```
Note: n=3 here, but n=2 in metafor::forest plot in PDF. Which is correct?


## Sensitivity Analysis
HKSJ correction results in narrower CIs:
```{r hksj atel}
pmhk.atelectasis <- metafor::rma(yi, vi, data=dat.atelectasis, method="PM", test="knha")
metafor::forest(pmhk.atelectasis,
                atransf=exp,
                at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 1, 2, 5, 10)),
                ilab = cbind(ai_atel, n1i, bi_atel, n2i),
                ilab.xpos = c(-9.5,-8.5,-7.5,-6.5),
                cex=.75, header=c("Author(s) and Year"),
                xlab=""
)
text(c(-9.5,-8.5,-7.5,-6.5), pmhk.atelectasis$k+1.5, c("E", "T", "E", "T"), cex=0.75)
text(c(-9,-7),     pmhk.atelectasis$k+2, c("Dexmed.", "Placebo"), cex=0.75)
par(xpd=NA)
text(log(c(0.001, 45)), -4, c("Favours Dexmedetomidine","Favours Placebo"), pos=c(4,2), offset=-0.5, cex=0.75)
```

```{r hksj pneu}
pmhk.pneumonia <- metafor::rma(yi, vi, data=dat.pneumonia, method="PM", test="knha")
metafor::forest(pmhk.pneumonia,
                atransf=exp,
                at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 1, 2, 5, 10)),
                ilab = cbind(ai_pneu, n1i, bi_pneu, n2i),
                ilab.xpos = c(-9.5,-8.5,-7.5,-6.5)+1.75,
                cex=.75, header=c("Author(s) and Year"),
                xlab=""
)
text(c(-9.5,-8.5,-7.5,-6.5)+1.75, pmhk.pneumonia$k+1.5, c("E", "T", "E", "T"), cex=0.75)
text(c(-9,-7)+1.75,     pmhk.pneumonia$k+2, c("Dexmed.", "Placebo"), cex=0.75)
par(xpd=NA)
text(log(c(0.005, 45)), -4, c("Favours Dexmedetomidine","Favours Placebo"), pos=c(4,2), offset=-0.5, cex=0.75)
```

```{r hksj hypox}
pmhk.hypoxemia <- metafor::rma(yi, vi, data=dat.hypoxemia, method="PM", test="knha")
metafor::forest(pmhk.hypoxemia,
                atransf=exp,
                at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 1, 2, 5, 10)),
                ilab = cbind(ai_hypo, n1i, bi_hypo, n2i),
                ilab.xpos = c(-7.5,-7,-6.5,-6)+1.75,
                cex=.75, header=c("Author(s) and Year"),
                xlab=""
)
text(c(-7.5,-7,-6.5,-6)+1.75, pmhk.hypoxemia$k+1.5, c("E", "T", "E", "T"), cex=0.75)
text(c(-7.25,-6)+1.75,     pmhk.hypoxemia$k+2, c("Dexmed.", "Placebo"), cex=0.75)
par(xpd=NA)
text(log(c(0.005, 40)), -3, c("Favours Dexmedetomidine","Favours Placebo"), pos=c(4,2), offset=-0.5, cex=0.75)
```

```{r hksj ARDS}
pmhk.ards <- metafor::rma(yi, vi, data=dat.ards, method="PM", test="knha")
metafor::forest(pmhk.ards,
                atransf=exp,
                at=log(c(0.002, 0.01, 0.03, 0.1, 0.4, 1, 2, 5, 10)),
                ilab = cbind(ai_ards, n1i, bi_ards, n2i),
                ilab.xpos = c(-9.5,-8.5,-7.5,-6.5)+1.75,
                cex=.75, header=c("Author(s) and Year"),
                xlab=""
)
text(c(-9.5,-8.5,-7.5,-6.5)+1.75, pmhk.ards$k+1.5, c("E", "T", "E", "T"), cex=0.75)
text(c(-9,-7)+1.75,     pmhk.ards$k+2, c("Dexmed.", "Placebo"), cex=0.75)
par(xpd=NA)
text(log(c(0.005, 45)), -3.5, c("Favours Dexmedetomidine","Favours Placebo"), pos=c(4,2), offset=-0.5, cex=0.75)
```


## Funnel plots
```{r funnels}
# Atelectasis:
### carry out trim-and-fill analysis
taf.atelectasis <- metafor::trimfill(pm.atelectasis)
### draw funnel plot with missing studies filled in
metafor::funnel(taf.atelectasis, legend=TRUE)
# OR and CI:
exp(taf.atelectasis$beta)
c(exp(taf.atelectasis$beta-taf.atelectasis$se), exp(taf.atelectasis$beta+taf.atelectasis$se))

# Pneumonia
taf.pneumonia <- metafor::trimfill(pm.pneumonia)
metafor::funnel(taf.pneumonia, legend=TRUE)
# OR and CI:
exp(taf.pneumonia$beta)
c(exp(taf.pneumonia$beta-taf.pneumonia$se), exp(taf.pneumonia$beta+taf.pneumonia$se))
```

Trim-and-fill analysis on the atelectasis meta-analysis data estimates that there 
are three studies missing. Removing the most extreme studies until there is no 
asymmetry results in a summary estimate of 0.60 (95% CI (0.41, 0.88)), which is
smaller but still statistically significant. However, we acknowledge that this 
procedure 
the total number of studies is small, 


